Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Break down the call to fit.

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{center}
\texttt{clf = LogisticRegression(penalty="l1").fit(X\_train, y\_train)}
\end{center}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence
enabling $\ell_1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

@@

Continuing with the previous example, predictions on unseen data
\texttt{X\_test}, \texttt{y\_test} can therefore be obtained and evaluated using
the following snippet:
\begin{center}
\texttt{y\_hat = clf.predict(X\_test)}\\
\texttt{score = clf.score(X\_test, y\_test)}
\end{center}

@@

In our example, if one wanted to transform the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X\_train = StandardScaler().fit(X\_train).transform(X\_train)}
\end{center}

>>>>

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{verbatim}
clf = LogisticRegression(penalty="l1")
clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence
enabling $\ell_1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}.

@@

Continuing with the previous example, predictions on unseen data
\texttt{X\_test}, \texttt{y\_test} can therefore be obtained and evaluated using
the following snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
score = clf.score(X_test, y_test)
\end{verbatim}

@@

In our example, if one wanted to transform the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{verbatim}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim}

Note that the snippet relies on the fact that the \texttt{fit} method always
returns the object it was called on , hence making method chaining  possible.
